A Closer Look at Time-Preserving paths on Evolving Graphs

### 2018-05-08 paper.tex
add motivation example part

\documentclass[12pt]{article}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{lipsum}
\usepackage[linesnumbered]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\makeatother
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\let\emptyset\varnothing
\definecolor{hotpink}{rgb}{0.9,0,0.5}
\definecolor{deepgray}{gray}{0.35}
\definecolor{deepgray2}{gray}{0.25}
\definecolor{deepgray3}{gray}{0.10}
\definecolor{lightgray}{gray}{0.95}
\definecolor{lightgray2}{gray}{0.85}
\definecolor{purple1}{RGB}{239,229,244}
\definecolor{purple2}{RGB}{216,191,216}
\definecolor{lightblue}{rgb}{0.73,0.33,0.83}
\definecolor{lightpurple}{rgb}{.8,.2,.8}
\definecolor{textcolor}{rgb}{0,0,5}
\definecolor{blue1}{RGB}{187,217,238}
\definecolor{blue2}{RGB}{235,244,250}
\definecolor{yellow1}{RGB}{255,255,102}
\definecolor{blue3}{RGB}{63,40,96}
\definecolor{red1}{RGB}{255, 102, 102}
\definecolor{green1}{RGB}{102, 255, 102}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\theoremstyle{definition}
\def\proof{\par{\bf Proof}. \ignorespaces}
\def\qedsymbol{\vbox{\hrule\hbox{%
                     \vrule height1.3ex\hskip0.8ex\vrule}\hrule}}
\def\endproof{\qquad\qedsymbol\medskip\par}

@@

\title{A Closer Look at Time-Preserving Walks on Evolving Graphs}

\author{Jiahao Chen and
Weijian Zhang
\thanks{%
  School of Mathematics,
The University of Manchester,
                Manchester, M13 9PL, England.
\texttt{weijian.zhang@manchester.ac.uk}.
}
}

@@

\begin{abstract}
This paper studies evolving graph centrality from the perspective of time-preserving walks. We describe time-preserving walks based on two dimensions of variation, namely static edges and causal edges.

@@

We study the impact of different time-preserving walks on node centrality by varying the edge weights of static and causal edges.
We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of an evolving graph model.
We construct an evolving coauthor network from a collection of research papers for the experiments.
\end{abstract}

@@

In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) travelled back in time and accidentally changed history.
However, we cannot travel back in time or even send a message to the past.
To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider time. In particular, a walk on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.

@@

% Related works
Researchers have generalised many static graph centrality algorithms for evolving graphs. One approach is to use the fact that the elements of the matrix product of adjacency matrices at different time stamps can correctly count the number of temporal walks.
However, not every centrality algorithm can be generalised in this way. Another approach is to define evolving graph centrality algorithms using time-respecting walks. This approach is applicable to algorithms that are defined using paths or walks.

@@

% our contribution this paper
Inspired by work
Borgatti noted in \cite{borgatti05} that the manner of traffic flow entails a new way to think about centrality.
where the author simulate different traffic flows to study centrality.

@@

\section{Time-Preserving walks}
\label{sec:time-pres-walks}

@@

We now describe time-preserving walks in more detail. We follow the definition of
\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.

@@

In \cite{tang10s}, a temporal shortest walk is measured in time units only, i.e., if node
$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
$v_i$ and $v_j$ is $k$. We can apply temporal breadth first
search (BFS) \cite{chen16} to discover the temporal walks and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.

If we use this definition of temporal walk for the temporal Katz centrality introduced in
\cite{grindrod11}, we have a new centrality measure.
In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal walks of length $1$, and
$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal walks of length $j -i$.
For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all walks of length 3.
In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
number of walks, i.e., longer walks has smaller effect to the overall rating.
Hence the final result is the summation of all products of the form
\[
\alpha^k A^{[i]} \cdots A^{[i+k]}
\]
% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.

Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest walks that traverse it.
We could extend
betweenness centrality on evolving graphs by replacing shortest walks with temporal shortest walks \cite{nicosia13}.
\begin{equation}
  \label{eq:bet1}
C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
\end{equation}
where $\alpha_{jk}$ represents the number of temporal shortest walks from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest walks from node $j$ to node $k$ that pass through the node $i$.

One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
\begin{equation}
  \label{eq:bet2}
  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
\end{equation}
where, as before, $\alpha_{j,k}$ represents the number of temporal shortest walks from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest walks from $j$ to $k$ in which node $i$ is traversed from
the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
average temporal betweenness of node $i$ is then defined as
$$
  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
$$
Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.

\subsection{Mapping from Evolving Graphs to Static Graphs}
\label{sec:centr-block-adjac}

@@

@@

In this section, we vary the edge
weights in both static and causal edges to study the impact of time-preserving walks on evolving graph centrality.
We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.

>>>>

\documentclass[12pt]{article}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{lipsum}

\usepackage{listings}

%%
%% Julia definition (c) 2014 Jubobs
%%
\lstdefinelanguage{Julia}%
  {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
      end,export,false,for,function,immutable,import,importall,if,in,%
      macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
      using,while},%
   sensitive=true,%
   alsoother={\$},%
   morecomment=[l]\#,%
   morecomment=[n]{\#=}{=\#},%
   morestring=[s]{"}{"},%
   morestring=[m]{'}{'},%
}[keywords,comments,strings]%

\lstset{%
    language         = Julia,
    basicstyle       = \ttfamily,
    keywordstyle     = \bfseries\color{blue},
    stringstyle      = \color{magenta},
    commentstyle     = \color{ForestGreen},
    showstringspaces = false,
}

\usepackage[linesnumbered]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}
\makeatother
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows}
\usetikzlibrary{snakes}
\usetikzlibrary{calc}
\let\emptyset\varnothing
\definecolor{hotpink}{rgb}{0.9,0,0.5}
\definecolor{deepgray}{gray}{0.35}
\definecolor{deepgray2}{gray}{0.25}
\definecolor{deepgray3}{gray}{0.10}
\definecolor{lightgray}{gray}{0.95}
\definecolor{lightgray2}{gray}{0.85}
\definecolor{purple1}{RGB}{239,229,244}
\definecolor{purple2}{RGB}{216,191,216}
\definecolor{lightblue}{rgb}{0.73,0.33,0.83}
\definecolor{lightpurple}{rgb}{.8,.2,.8}
\definecolor{textcolor}{rgb}{0,0,5}
\definecolor{blue1}{RGB}{187,217,238}
\definecolor{blue2}{RGB}{235,244,250}
\definecolor{yellow1}{RGB}{255,255,102}
\definecolor{blue3}{RGB}{63,40,96}
\definecolor{red1}{RGB}{255, 102, 102}
\definecolor{green1}{RGB}{102, 255, 102}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\theoremstyle{definition}
\def\proof{\par{\bf Proof}. \ignorespaces}
\def\qedsymbol{\vbox{\hrule\hbox{%
                     \vrule height1.3ex\hskip0.8ex\vrule}\hrule}}
\def\endproof{\qquad\qedsymbol\medskip\par}

@@

\title{A Closer Look at Time-Preserving paths on Evolving Graphs}

\author{Jiahao Chen \thanks{
Capital One,
New York, USA.
\texttt{cjiahao@gmail.com}
}
 and
Weijian Zhang
\thanks{%
  School of Mathematics,
The University of Manchester,
                Manchester, M13 9PL, England.
\texttt{weijian.zhang@manchester.ac.uk}.
}
}

@@

\begin{abstract}
This paper studies evolving graph centrality from the perspective of time-preserving paths. We describe time-preserving paths based on two dimensions of variation, namely static edges and causal edges.

@@

We study the impact of different time-preserving paths on node centrality by varying the edge weights of static and causal edges.
We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of an evolving graph model.
We construct an evolving coauthor network from a collection of research papers for the experiments.
\end{abstract}

@@

In the 1985 science-fiction film ``Back to the Future'', Marty McFly (played by Michael J. Fox) travelled back in time and accidentally changed history.
However, we cannot travel back in time or even send a message to the past.
To traverse an evolving graph, a.k.a a time-dependent graph, one has to consider order of time stamps. In particular, a walk on an evolving graph needs to be time-preserving, meaning a node can not pass a massage (through an edge) to a node at a earlier time.

@@

% Related works
Researchers have generalised many static graph centrality algorithms for evolving graphs. One approach is to use the fact that the elements of the matrix product of adjacency matrices at different time stamps can correctly count the number of temporal paths.
However, not every centrality algorithm can be generalised in this way. Another approach is to define evolving graph centrality algorithms using time-respecting paths. This approach is applicable to algorithms that are defined using paths or paths.

@@

% our contribution this paper
Inspired by Borgatti's work \cite{borgatti05} on simulating different flow process on static graphs, we

Borgatti noted in  that the manner of traffic flow entails a new way to think about centrality.
where the author simulate different traffic flows to study centrality.

@@

\section{Motivation: A Closer Look at Katz Centrality on Evolving Graphs}
\label{sec:motivation}

We let $G_n = \langle G^{[1]}, G^{[2]}, \ldots, G^{[n]} \rangle$ be an evolving graph
and $A^{[1]}, A^{[2]}, \dots A^{[n]}$ be the corresponding adjacency matrices.
Then the dynamic communicability matrix is defined as
\begin{equation}
  \label{eq:q}
  Q^{[k]} = (I - \alpha A^{[1]})^{-1}(I - \alpha A^{[2]})^{-1} \cdots (I -  \alpha A^{[n]})^{-1},
\end{equation}
where parameter $\alpha < 1/ \max_k \rho(A^{[k]})$, the spectral radius of $A^{[k]}$.
The $i$th row sum of $Q^{[k]}$ is the broadcast centrality.

Suppose $A$, $B$, and $C$ are three co-workers in a large internet company. Figure \ref{fig:katz_eg}
shows how they exchange ideas during $3$ days at work. The directions of the arrows indicate the direction of the flow of ideas.
For example, $A$ shares a new idea with $B$ on day $1$ and $B$ shares a new idea with $C$ on dat $3$. As a result, $A$'s idea can influence $C$.

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.38, line width =1.5pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {B};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {C};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {A};
  \node[circle,fill=green1, minimum size=0.2cm] (n6) at (3,7) {B};
  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {C};
  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {A};
   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {B};
  \node[circle,fill=green1, minimum size=0.2cm] (n12) at (6,5)  {C};
  \node[circle,draw=red1, minimum size=0.2cm] (n14) at (8,10) {A};
  \foreach \from/\to in {n10/n7, n1/n4, n4/n1, n11/n12, n1/n6}
   \draw[every edge,->] (\from) -- (\to);
 %\draw[dotted,->](n4) -- (n12);
% \draw[dotted,->](n7) to[out=80, in=40](n11);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{$2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges in each time stamp are shown as black arrows.}
\label{fig:katz_eg}
\end{figure}

We could use EvolvingGraphs.jl to generate the above evolving graph and compute the Katz centrality.

\begin{lstlisting}
using EvolvingGraphs
using EvolvingGraphs.Centrality

g = EvolvingGraph{Node{String}, Int}()
add_bunch_of_edges!(g, [("A", "B", 1), ("A", "C", 2),
("A", "B", 2),("C", "A", 2),("B", "C", 3)])
\end{lstlisting}

The centrality values for each node are
\begin{lstlisting}
katz(g)
3-element Array{Tuple{EvolvingGraphs.Node{String},Float64},1}:
 (Node(A), 0.742301)
 (Node(B), 0.42943)
 (Node(C), 0.514373)
\end{lstlisting}

As expected $A$ is the most important node in the network. $C$ is the second important node in the network as it influenced
$A$ at time stamp $2$. If we reverse the time of communication between day $1$ and $3$, i.e., $B$ shares a new idea with $C$ on day $1$ and $A$ shares a new idea with $B$ on day $3$. Then the idea $A$ had on day $3$ can not pass to $C$ in this case. This is illustrated in Figure \ref{fig:katz_eg2}.

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.38, line width =1.5pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {B};
  \node[circle,fill=green1, minimum size=0.2cm] (n8) at (-10,5) {C};
  \node[circle,draw=red1, minimum size=0.2cm] (n10) at (-8,10) {A};
  \node[circle,fill=green1, minimum size=0.2cm] (n6) at (3,7) {B};
  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {C};
  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {A};
   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {B};
  \node[circle,draw=red1, minimum size=0.2cm] (n12) at (6,5)  {C};
  \node[circle,fill=green1, minimum size=0.2cm] (n14) at (8,10) {A};
  \foreach \from/\to in {n7/n8, n1/n4, n4/n1, n1/n6, n14/n11}
   \draw[every edge,->] (\from) -- (\to);
 %\draw[dotted,->](n4) -- (n12);
% \draw[dotted,->](n7) to[out=80, in=40](n11);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $3$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges in each time stamp are shown as black arrows.}
\label{fig:katz_eg2}
\end{figure}

In this cast, we have
\begin{lstlisting}
g2 = EvolvingGraph{Node{String}, Int}()
add_bunch_of_edges!(g2, [("A", "B", 3), ("A", "C", 2),
("A", "B", 2),("C", "A", 2),("B", "C", 1)])
\end{lstlisting}

The centrality ratings of the three nodes are

\begin{lstlisting}
katz(g2)
3-element Array{Tuple{EvolvingGraphs.Node{String},Float64},1}:
 (Node(A), 0.687679)
 (Node(B), 0.490062)
 (Node(C), 0.535666)
\end{lstlisting}

Notice the rating of $A$ decreased as its influence is not as important as in Figure \ref{fig:katz_eg}.

% does not take account of walks in a long time. cost in time
If the final communication between $A$ and $B$ are not on day $3$ but on day $100$, as shown in Figure \ref{fig:katz_eg3},
we would expect the centrality ratings to change. However, according to \eqref{eq:q}, ratings are unchanged.
We notice that the generalised Katz centrality on evolving graphs only takes account of the edges at each time stamp but not the communication time between edges at different time stamps.

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.38, line width =1.5pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {B};
  \node[circle,fill=green1, minimum size=0.2cm] (n8) at (-10,5) {C};
  \node[circle,draw=red1, minimum size=0.2cm] (n10) at (-8,10) {A};
  \node[circle,fill=green1, minimum size=0.2cm] (n6) at (3,7) {B};
  \node[circle,fill=green1, minimum size=0.2cm] (n4) at (-2,5) {C};
  \node[circle,fill=green1, minimum size=0.2cm] (n1) at (0,10) {A};
   \node[circle,fill=green1, minimum size=0.2cm] (n11) at (11,7) {B};
  \node[circle,draw=red1, minimum size=0.2cm] (n12) at (6,5)  {C};
  \node[circle,fill=green1, minimum size=0.2cm] (n14) at (8,10) {A};
  \foreach \from/\to in {n7/n8, n1/n4, n4/n1, n1/n6, n14/n11}
   \draw[every edge,->] (\from) -- (\to);
 %\draw[dotted,->](n4) -- (n12);
% \draw[dotted,->](n7) to[out=80, in=40](n11);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $100$};
    \end{tikzpicture}
\end{center}
\caption{An evolving directed graph with 3 time stamps $1$, $2$ and $100$.
At each time stamp, the evolving graph is represented as a graph.
The green filled circles represent active nodes while the red circles represent
inactive nodes. Directed edges in each time stamp are shown as black arrows.}
\label{fig:katz_eg3}
\end{figure}

\section{Time-Preserving paths}
\label{sec:time-pres-paths}

@@

We now describe time-preserving paths in more detail. We follow the definition of
\emph{evolving graph}, \emph{temporal node} and \emph{active node} in \cite{chen16}.

@@

\subsection{Evolving Graphs and Static Graphs}
\label{sec:centr-block-adjac}

We can not simply use static graphs to replace evolving graphs for two main reasons.
First, a path has to preseve the dimension, i.e., certain path is incorrect in the aggregated static graph.
Second, two path between $A$ and $B$ are considered to be one path in the aggregated static graph.

@@

In \cite{tang10s}, a temporal shortest walk is measured in time units only, i.e., if node
$v_i$ can reach node $v_j$ in $k$ time steps then the distance between node
$v_i$ and $v_j$ is $k$. We can apply temporal breadth first
search (BFS) \cite{chen16} to discover the temporal paths and then only take account of the temporal difference between the first node $(v_1, t_1)$ and the last node $(v_n, t_n)$, i.e., $t_n - t_1$.

If we use this definition of temporal walk for the temporal Katz centrality introduced in
\cite{grindrod11}, we have a new centrality measure.
In the matrix form, the nonzero entries of $A^{[t_i]} A^{[t_{i+1}]}$ counts all the temporal paths of length $1$, and
$A^{[t_i]}\cdots A^{[t_j]}$, where $i < j$ counts all the temporal paths of length $j -i$.
For example, $A^{[1]}A^{[4]}$, $A^{[1]}A^{[1]}A^{[4]}$ and $A^{[1]}A^{[2]}A^{[3]}A^{[4]}$ are all paths of length 3.
In the original Katz centrality, the `attenuation' factor $\alpha$ is imposed on the
number of paths, i.e., longer paths has smaller effect to the overall rating.
Hence the final result is the summation of all products of the form
\[
\alpha^k A^{[i]} \cdots A^{[i+k]}
\]
% Note this can not be written in \eqref{eq:katz}, as discussed in Section \ref{sec:temp-katz-centr}.

% can not simply aggregate nodes: introduce wrong paths.

Note that the $(i,j)$th element of adjacency matrix $A^k$ counts the only of paths from $i$ to $j$.
To simulate a Katz centrality,
the shortest path algorithms search through all possible paths between $i$ and $j$.

Recall that betweenness centrality of a node in a static graph is defined by counting the fraction of shortest paths that traverse it.
We could extend
betweenness centrality on evolving graphs by replacing shortest paths with temporal shortest paths \cite{nicosia13}.
\begin{equation}
  \label{eq:bet1}
C_i^{betweenness} = \sum_{j \in V}\sum_{k \in V, k \ne j}\frac{\alpha_{jk}(i)}{\alpha_{jk}},
\end{equation}
where $\alpha_{jk}$ represents the number of temporal shortest paths from node $j$ to node $k$ and $\alpha_{jk}(i)$ represents the number of temporal shortest paths from node $j$ to node $k$ that pass through the node $i$.

One may want to take into account the length of time a node passes a message. The temporal betweenness centrality of the node $i$ at time stamp $t_m$ is defined as
\begin{equation}
  \label{eq:bet2}
  C_i^{betweenness}(t_m) = \sum_{j\ne i}\sum_{k\ne j, k\ne i}\frac{U_{j,k,t_m}(i)}{\alpha_{j,k}},
\end{equation}
where, as before, $\alpha_{j,k}$ represents the number of temporal shortest paths from $j$ to $k$ and $U_{j,k,t_m}(i)$ represents the number of temporal shortest paths from $j$ to $k$ in which node $i$ is traversed from
the walk in the time stamp $t_m$ or a previous time stamp $t_{m-1}$. Then
average temporal betweenness of node $i$ is then defined as
$$
  C_i^{betweenness} = \frac{1}{M}\sum_m C_i^{betweenness}(t_m).
$$
Note \eqref{eq:bet1} only takes account of static edges while \eqref{eq:bet2} takes account of both static edges and causal edges.

@@

In this section, we vary the edge
weights in both static and causal edges to study the impact of time-preserving paths on evolving graph centrality.
We also compare evolving graph centrality with the aggregated static graph case to gain insight about the advantage of evolving graph model.
